---
title: "Lab 7"
author: "Shelby Oliver"
date: "March 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Install necessary libraries and files

```{r}
library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(spatstat)
library(maptools)
library(corrplot)

#read in the data
oil<-read.csv("oil_spills.csv")
```

##Column graph to look at oil spills in Texas

```{r}
oil_df<-oil %>% 
  filter(`Accident.State`=='TX'&`Accident.Year`,2017) %>% #have to use special ` to call the column when it has a space in the name
  group_by(`Accident.Year`) %>% 
  summarise(Loss = sum(Net.Loss..Barrels.))

colnames(oil_df)<- c("YR","OilLoss")

#make the column graph
ggplot(oil_df, aes(x = YR, y = OilLoss))+geom_col()+theme_classic()
```


## Convert oil spill information into spatial information. Make leaflet plot of oilspills in Texas in 2016

```{r}
oil_loc<-oil %>% 
  filter(`Accident.State`=="TX"&`Accident.Year`==2016) %>% 
  select(Latitude, Longitude, Net.Loss..Barrels.)

colnames(oil_loc)<- c( "lat","long","oil_loss")

#need to tell R that you are working with spatial information. currently, R is just seeing this information as a dataframe. Change it so that it turns into spatial data.

oil_spatial<- st_as_sf(oil_loc, coords=c('long','lat'), crs=4326)

#now make a leaflet map of the data

leaflet(oil_spatial) %>% 
  addTiles() %>%  #add a basemap
  addMarkers()

```

## tmap plot with the Texas state shapefile

```{r}
states<- st_read( dsn = ".", layer = 'states') 
texas_bord<-states %>% 
  filter(STATE_NAME == "Texas") %>% 
  st_transform(4326)
st_crs(texas_bord)#tells you your coordinate reference system

plot(texas_bord)
tm_shape(texas_bord)+
  tm_polygons()+
  tm_shape(oil_spatial)+
  tm_dots(size = 0.3)

```


###Convert the data to spatial points patterns with combination of point data and the bounding window

##Does this point pattern follow csr? (Is the distribution of oil spills in TX spatially random or not?) Use point pattern analysis

```{r}
#convert back from simple features to a dataframe

spill_sp<-as(oil_spatial, "Spatial")
spill_ppp<-as(spill_sp, "ppp")#convert from dataframe to the point pattern

texas_spatial<-as(texas_bord, "Spatial")
texas_outerwindow<- as(texas_spatial, "owin")#create spatial window to bound the point pattern analysis

all_ppp<-ppp(spill_ppp$x, spill_ppp$y, window = texas_outerwindow)

```

## A density plot:

```{r}
plot(density(all_ppp), sigma=0.4)#sigma is important and can change your interpretation of your results, You need to select a sigma value (bandwidth) that makes sense for the data
```

### Quadrat test for spatial evenness
oil_qt<- quadrate.test(all_ppp, nx = 5, ny = 5)#ny and nx specify the number of regions in either direction
